%------------------------
% Resume Template
% Author : Dhruv Koli
% License : MIT
%------------------------


\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins and spacing
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\color{Black}\scshape\raggedright\Large
}{}{0em}{}[\color{Black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\normalsize{
        {#1 #2 #3 #4 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\normalsize #2} \\
      \textit{\normalsize#3} & \textit{\normalsize #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\normalsize#1} & \textit{\normalsize #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \normalsize#1 & \textbf{\normalsize #2}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\myUrl}[1]{\texttt{\href{#1}{\nolinkurl{#1}}}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {\Huge \scshape Dhruv Koli} & \small Email: \href{mailto:googldhruv@gmail.com}{\texttt{googldhruv@gmail.com}} \\
  \small \myUrl{https://dask-58.github.io} & \small Mobile:~+91-7823080783 \\
  \small \texttt{\myUrl{https://github.com/dask-58}} \\
\end{tabular*}

\vspace{-5pt}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Information Technology, Dharwad}{Aug 2023 -- Present}
{B.Tech. in Computer Science \& Engineering -- 8.41 CPI}{Dharwad, KA, India}
 {\normalsize \textit{ \normalsize{\newline{}\textbf{Courses:} Probability, Discrete Mathematics, Data Structures and Algorithms.}}}
\resumeSubheading
{PM Shri Kendriya Vidyalaya, C.R., Solapur}{Apr 2011 -- May 2021}
{Primary \& Secondary Schooling}{Solapur, MH, India}
{\normalsize \textit{ \normalsize{\newline{}\textbf{Subjects:} Mathematics, Physics \& Chemistry, Social Science, }}}
\resumeSubHeadingListEnd

\vspace{-5pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{None}{}{}{}
\resumeSubHeadingListEnd

\vspace{-5pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{Erudite -- GenAI Web App}{\href{https://dask-58.github.io/erudite}{LIVE}}{WebDesign, GitHub Actions, React + Vite, Typescript, TailwindCSS}{Jan 2024}
\resumeItemListStart
    \resumeItem{
      Developed a dynamic web application with React, utilizing Vite and Tailwind CSS for efficient build processes and modern styling. Integrated the Google Gemini Pro Model API to provide real-time AI-powered responses to user text inputs, enhancing the app's interactivity and functionality.
    }
\resumeItemListEnd

\resumeSubheading
{Fortune-Spender Web Game}{\href{https://dask-58.github.io/spendelonmoney}{LIVE}}
{Javascript, HTML5, CSS3}{Nov 2023}
\resumeItemListStart
    \resumeItem{
      Developed an engaging web-based game using JavaScript, HTML5, and CSS3. Designed the game to be interactive and visually appealing, with responsive design for various devices. Successfully launched the game, which received positive user feedback for its functionality and entertainment value.
    }
\resumeItemListEnd

\resumeSubheading
{Personal Portfolio \& Blog}{\href{https://dask-58.github.io}{LIVE}}
{Vue, Astro, Typescript, GitHub Pages \& Actions}{Sep 2023}
\resumeItemListStart
    \resumeItem{
      Built a portfolio and blog using Astro and Vue, designed to showcase projects, share articles on computer science and AI, and document personal experiences. The platform features a clean, user-friendly interface and dynamic content management.
    }
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-5pt}
%-----------ACHIEVEMENTS-----------
\vspace{-5pt}
\section{Programming Achievements}
\begin{description}[font=$\bullet$]
\item {Rated \textbf{Pupil} on Codeforces: Participated in \textbf{37} contests \& attained a peak rating of \textbf{1350}.}
\vspace{-5pt}
\item {Rated \textbf{3-star} on CodeChef: Participated in \textbf{18} contests \& attained a peak rating of \textbf{1703}.}
\vspace{-5pt}
\item {Top \textbf{8\%} on Leetcode: Participated in \textbf{9} contests \& attained a peak rating of \textbf{1782}.}
\vspace{-5pt}
\item {Winner of \textbf{Google DSC} ML Contest training a model with \textbf{99.9988 \% } accuracy.}
\vspace{-5pt}
\item {Passed the \textbf{Hackerrank Problem Solving (Intermediate)} assessment.}
\end{description}

%-----------VOLUNTEERING-----------
\section{Volunteering}
\resumeSubHeadingListStart
    \resumeSubheading
      {Return 0}{April 2024 - Present}
      {Problem Setter - The Programming Club of IIIT DWD}{}
    \resumeItemListStart
        \resumeItem{Created and curated diverse programming problems for contests.}
        \resumeItem{Mentored and guided students, enhancing their coding skills and problem-solving abilities.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


% \vspace{-5pt}
%-----------SKILLS AND INTERESTS-----------
\section{Skills \& Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
        \textbf{Languages}:~~~~~~~C/C++, Python, \LaTeX, Kotlin, Lua, Bash, JavaScript, Typescript, Swift. \\
        \textbf{Frameworks}:~~~~~Vue, Astro, React, Vite, UnoCSS, Tailwind \\
        \textbf{Dev Tools}:~~~~~~~ Vim/Neovim, VSCode, Sublime. \\
        \textbf{NonTech}:~~~~~~~~ Football
    }
\end{itemize}

\end{document}
